The {TestIdeals} package for \emph{Macaulay2}

### 2018-10-19 Fsing/TestIdealsPaper/TestIdeals.tex
Removed TakTak08 reference as I believe equivalent statements were known decades earlier.

\begin{definition}
Let $K$ be an $F$--finite field of prime characteristic $p,$ and let
$f\in R=K[x_1,\ldots, x_d].$ We define the \emph{level of} $f$ as the
smallest possible integer $e$ where the descending chain
\[
R=(f^{p^0-1})^{[1/p^0]}\supseteq (f^{p-1})^{[1/p]}\supseteq
(f^{p^2-1})^{[1/p^2]}\supseteq\ldots%\supseteq (f^{p^{i-1}-1})^{[1/p^{i-1}]}
\supseteq (f^{p^i-1})^{[1/p^i]}\supseteq\ldots
\]
stabilizes.
\end{definition}
This invariant was introduced in \cite{AlvarezBlickleLyubeznik2005}.  It is also essentially the same data as the HSLG-number of the pair $(R, f^1)$ as computed in (4) above (it is that number $+1$).
One interesting particular
case is when $K=\mathbb{F}_p$ and $f$ is the defining homogeneous polynomial of a hyperelliptic curve
of genus $g;$ when $g=1,$ it was proved in
\cite{BoixDeStefaniVanzo2015} that the corresponding elliptic curve defined by $f$
is ordinary if and only if its level is $1,$ (equivalently, if and only if
$(R/(f))_{(x,y,z)}$ is $F$--pure% \cite{TakTak08}
) and supersingular if and only if its level is $2.$ When
the genus is at least $2,$ level $2$ is a necessary (but not sufficient) condition for the curve
for being ordinary \cite{BlancoBoixFordhamYilmaz2018}; in this case, one also
has that, if the curve is supersingular, then its level has to be at least $3,$ so the level can
always distinguish these two properties in any genus. We illustrate these results by means
of the following examples.

>>>>

\begin{definition}
Let $K$ be an $F$--finite field of prime characteristic $p,$ and let
$f\in R=K[x_1,\ldots, x_d].$ We define the \emph{level of} $f$ as the
smallest possible integer $e$ where the descending chain
\[
R=(f^{p^0-1})^{[1/p^0]}\supseteq (f^{p-1})^{[1/p]}\supseteq
(f^{p^2-1})^{[1/p^2]}\supseteq\ldots%\supseteq (f^{p^{i-1}-1})^{[1/p^{i-1}]}
\supseteq (f^{p^i-1})^{[1/p^i]}\supseteq\ldots
\]
stabilizes.
\end{definition}
This invariant was introduced in \cite{AlvarezBlickleLyubeznik2005}.  It is also essentially the same data as the HSLG-number of the pair $(R, f^1)$ as computed in (4) above (it is that number $+1$).
One interesting particular
case is when $K=\mathbb{F}_p$ and $f$ is the defining homogeneous polynomial of a hyperelliptic curve
of genus $g;$ when $g=1,$ it was proved in
\cite{BoixDeStefaniVanzo2015} that the corresponding elliptic curve defined by $f$
is ordinary if and only if its level is $1,$ (equivalently, if and only if
$(R/(f))_{(x,y,z)}$ is $F$--pure, %this was already proved by Takagi and Takahashi in \cite{TakTak08}
) and supersingular if and only if its level is $2.$ When
the genus is at least $2,$ level $2$ is a necessary (but not sufficient) condition for the curve
for being ordinary \cite{BlancoBoixFordhamYilmaz2018}; in this case, one also
has that, if the curve is supersingular, then its level has to be at least $3,$ so the level can
always distinguish these two properties in any genus. We illustrate these results by means
of the following examples.
